Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
setwd("~/R/udacity scripts/lesson4")
library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv',sep='\t')

qplot(x = age, y = friend_count, data = pf)
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point()

summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/20) +
  xlim(13,90)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20, position = position_jitter(h=0)) +
  xlim(13, 90) +
  coord_trans(y = "sqrt")

```


### Relationship between friendships initiated and age

```{r}
ggplot(aes(x = age, y = friendships_initiated), data = pf) + 
  geom_point(alpha = 1/40, position = position_jitter(h=0)) +
  xlim(13, 90) +
  coord_trans(y="sqrt")
```

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)
fc_by_age <- pf %>% 
  group_by(age) %>% 
  summarise(friend_count_mean = mean(friend_count),friend_count_median=median(friend_count),n=n()) %>% 
  arrange(age)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = age, y = friend_count_mean), data = fc_by_age) +
  geom_line() +
  xlim(13, 90) +
  ylim(0, 500)
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r, fig.width=10, fig.height=5}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20,
             position = position_jitter(h=0),
             color='orange') +
  coord_trans(y = "sqrt",limx = c(13,70),limy = c(0,1000)) +
  geom_line(stat='summary', fun.y = mean) +
  geom_line(stat='summary', fun.y = quantile, fun.args = list(probs = .9), colour='blue', linetype = 2) +
  geom_line(stat='summary', fun.y = quantile, fun.args = list(probs = .5), colour='black', linetype = 2) +
  geom_line(stat='summary', fun.y = quantile, fun.args = list(probs = .1), colour='blue', linetype = 2)
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(x=pf$age,y=pf$friend_count,method="pearson")
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(aes(x = www_likes_received, y = likes_received),data=pf) +
  geom_point(alpha = 1/50, position='jitter') +
  xlim(0, quantile(pf$www_likes_received, 0.95)) +
  ylim(0,quantile(pf$likes_received, 0.95))
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
with(pf,cor.test(x = www_likes_received, y = likes_received, method ='pearson'))
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
library(alr3)
data("Mitchell")
```

Create your plot!

```{r Temp vs Month}
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
  geom_point()
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
with(Mitchell,cor.test(x = Month, y = Temp, method ='pearson'))
```

***

### Making Sense of Data
Notes:

```{r, fig.width = 14, fig.height = 6}
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
  geom_point() +
  scale_x_continuous(breaks=seq(0,204,12))
```

```{r, fig.width = 12, fig.height = 6}
ggplot(aes(x=(Month%%12),y=Temp),data=Mitchell)+ 
  geom_point() 
```



***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(aes(x = age, y = friend_count_mean), data = fc_by_age) +
  geom_line() +
  xlim(13, 90) +
  ylim(0, 500)
```

***

### Age with Months Means

```{r Age with Months Means}
pf$age_with_months <- pf$age + (1 - pf$dob_month / 12)
```

Programming Assignment
```{r Programming Assignment}
pf.fc_by_age_months <- pf %>% 
  group_by(age_with_months) %>% 
  summarise(friend_count_mean = mean(friend_count),friend_count_median=median(friend_count),n=n()) %>% 
  arrange(age_with_months)

ggplot(aes(x = age_with_months, y = friend_count_mean), data = pf.fc_by_age_months) +
  geom_line() +
  xlim(13, 71) +
  ylim(0, 500)
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection: I learned how to do scatterplots in order to see the relationship between two variables. I learned how to use alpha (transparency) and jitter to get a better visualization of the data and avoid overplotting. I learned how to summarise dataframes and plot conditional means and quantiles to get a quick sense of the dispersion of the data. I learned that a weak correlation coefficient doesn't necessarily mean that the variables are not correlated and vice versa. I learned that I have to put the data into perspective in order to get a better sense of it. I learned that we can choose several different granularities for the data we're plotting and each one of them can provide us a different insight (bias x variance tradeoff).

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

